Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-02 paper/paper.tex
fix ref
pass IV.C5

\subsubsection{Weight Optimization}
\label{sec:weight-optimization}
We optimized the weights of these heuristic functions as follows. We
ran \tname{} using different combinations of weights on a sample of
attacks and chose the combination that offered the best overall
performance, which we computed with the sum of the rankings of the
golden rule on each attack. The weight combination that led to the
smaller sum of rankings was considered the best choice. We considered
\emph{all} combinations of the following weights 0, 0.25, 0.5, 0.75,
and 1. Given that there are four different functions and five possible
weight values, we needed to run \tname{} on the sample of attacks for
625 (=$5^4$) times. In the end of the process, the weight combination
$\langle{}1,0.25,0.25,1\rangle$ was the best choice we found. Although
results showed that this strategy results in good performance, we
remain to evaluate other optimization strategies to find better
weights.

@@

options. Kao~\etal~\cite{kao2015AutomaticNR} proposed ARGS, a system

>>>>

\subsubsection{Weight Optimization}
\label{sec:weight-optimization}
We optimized the weights of these heuristic functions as follows. We
ran \tname{} using different combinations of weights on a sample of
attacks and chose the combination that offered the best overall
performance, which we computed with the sum of the rankings of the
golden rule on each attack. The weight combination that led to the
smaller sum of rankings was considered the best choice. We considered
\emph{all} combinations of the following weights 0, 0.25, 0.5, 0.75,
and 1. Given that there are four different functions and five possible
weight values, we needed to run \tname{} on the sample of attacks for
625 (=$5^4$) times. In the end of the process, the weight combination
$\langle{}1,0.25,0.25,1\rangle$ was the best choice we found. Although
results showed that this strategy results in good performance, we
remain to evaluate other optimization strategies to find better
weights. \Gui{We used Differential Evolution algorithm from SciPy to find the best weights for our set of attacks. The optmization for our weights consists of minimizing the function that returns the sum of every attack's golden rule ranking in our set given a combination of weights. 
\indent
$\sum_{i=1}^{N}\mathit{R_i}$ ($\mathit{R_i}$, where $\mathit{R}$ is the ranking of a golden rule and $\mathit{N}$ is the number of attacks)
The algorithm also receives as input the range which the weights can change (between 0 and 1) and the max number of generations, which we set to 10 (setting higher values could provide better results, but also would take more time). At the end, the optimization returned the weights [0.28058353, 0.05713404, 0.043285, 0.49022223]}

@@

options. Kao~\etal~\cite{Kao2015AutomaticNR} proposed ARGS, a system
